Compilation and Backend-Independent Vectorization for Multi-Party Computation

### 2022-04-26 overleaf/paper_SIMD.tex
Changed title (feel free to suggest better ones) and affiliations.

%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title[Scheduling and Vectorization for MPC]{Scheduling and Vectorization for MPC}

@@

\author{Muhammad Ishaq}
\authornote{This work was done in part while the author was at RPI.}
\email{m.ishaq@ed.ac.uk}
%\orcid{1234-5678-9012}
%\author{G.K.M. Tobin}
%\authornotemark[1]
%\email{webmaster@marysville-ohio.com}
\affiliation{%
    \institution{University of Edinburgh}
    %\streetaddress{P.O. Box 1212}
    \city{Edinburgh}
    \state{Scotland}
%    \postcode{43017-6221}
}

\author{Lindsey Kennard}
\email{kennal@rpi.edu}
\affiliation{%
    \institution{Rensselaer Polytechnic Institute}
    %\streetaddress{1 Th{\o}rv{\"a}ld Circle}
    \city{Troy}
    \state{New York}
    %\country{Iceland}
}

@@

\author{Vassilis Zikas}
\authornote{This work was done in part while the author was visiting UCLA and supported in part by DARPA and SPAWAR under contract N66001-15-C-4065 and by a SICSA Cyber Nexus Research Exchanges grant.}
\email{vzikas@inf.ed.ac.uk}
%\orcid{1234-5678-9012}
%\author{G.K.M. Tobin}
%\authornotemark[1]
%\email{webmaster@marysville-ohio.com}
\affiliation{%
    \institution{University of Edinburgh}
    %\streetaddress{P.O. Box 1212}
    \city{Edinburgh}
    \state{Scotland}
    %    \postcode{43017-6221}
}

>>>>

%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title[Compilation and Backend-Independent Vectorization for Multi-Party Computation]{Compilation and Backend-Independent Vectorization for Multi-Party Computation}

@@

\author{Muhammad Ishaq}
%\authornote{This work was done in part while the author was at RPI.}
\email{ishaqm@purdue.edu}
%\orcid{1234-5678-9012}
%\author{G.K.M. Tobin}
%\authornotemark[1]
%\email{webmaster@marysville-ohio.com}
\affiliation{%
    \institution{Purdue University}
    %\streetaddress{P.O. Box 1212}
    \city{West Lafayette}
    \state{Indiana}
%    \postcode{43017-6221}
}

\author{Lindsey Kennard}
\email{fire.elemental@gmail.com}
\affiliation{%
    \institution{STR}
    %\streetaddress{1 Th{\o}rv{\"a}ld Circle}
    \city{Boston}
    \state{Massachusets}
    %\country{Iceland}
}

@@

\author{Vassilis Zikas}
%\authornote{This work was done in part while the author was visiting UCLA and supported in part by DARPA and SPAWAR under contract N66001-15-C-4065 and by a SICSA Cyber Nexus Research Exchanges grant.}
\email{vzikas@purdue.edu}
%\orcid{1234-5678-9012}
%\author{G.K.M. Tobin}
%\authornotemark[1]
%\email{webmaster@marysville-ohio.com}
\affiliation{%
    \institution{Purdue University}
    %\streetaddress{P.O. Box 1212}
    \city{West Lafayette}
    \state{Indiana}
    %    \postcode{43017-6221}
}
